Bayesian Inference from Time Series: Information Loss and the Whittle Likelihood

### 2018-03-06 doc/ms.tex
New result

\begin{table}[!ht]
\centering
\begin{tabular}{@{}l@{\hspace{3em}}l@{\hspace{2em}}l@{}}
\toprule
$N$         &       Likelihood      &  Mut. Inf. (nats) \\
\hline
20          &       Exact           & \\
20          &       Whittle         & $1.491 \pm 0.055$\\ 
50          &       Exact           & \\
50          &       Whittle         & $1.957 \pm 0.055$ \\
100         &       Exact           & $2.605 \pm 0.053$ \\
100         &       Whittle         & $2.052 \pm 0.055$ \\
200         &       Exact           &   \\
200         &       Whittle         &   \\
\bottomrule
\end{tabular}
\caption{The mutual information between the data and the log-period, for
different numbers of datapoints $N$ and for different likelihoods (exact vs.
Whittle).
This is equal to the prior expected reduction in the entropy
in going from the prior to the posterior.\label{tab:oscillation_results}}
\end{table}

>>>>

\begin{table}[!ht]
\centering
\begin{tabular}{@{}l@{\hspace{3em}}l@{\hspace{2em}}l@{}}
\toprule
$N$         &       Likelihood      &  Mut. Inf. (nats) \\
\hline
20          &       Exact           & $1.930 \pm 0.055$ \\
20          &       Whittle         & $1.491 \pm 0.055$\\ 
50          &       Exact           & \\
50          &       Whittle         & $1.957 \pm 0.055$ \\
100         &       Exact           & $2.605 \pm 0.053$ \\
100         &       Whittle         & $2.052 \pm 0.055$ \\
200         &       Exact           &   \\
200         &       Whittle         &   \\
\bottomrule
\end{tabular}
\caption{The mutual information between the data and the log-period, for
different numbers of datapoints $N$ and for different likelihoods (exact vs.
Whittle).
This is equal to the prior expected reduction in the entropy
in going from the prior to the posterior.\label{tab:oscillation_results}}
\end{table}
